Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-23 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
Minor edits in sec 4

In this work, we choose $L$ such that the domain $\Omega = \left[-L, L\right]$ will include the smallest interval that contains all the inputs points $x_i$. Without loss of generality, we can assume all data points are contained in a symmetric interval around zero. Let $S = \max_{i}|x_i|$, then it follows that $x_i \in \left[-S, S\right]$ for all $i$. We now define $L$ as
\begin{equation}\label{eq_boundary}
L=c \cdot S,
\end{equation} 
%
where $S > 0$ represents the half-range of the input space, and $c \geq 1$ is the proportional extension factor. In the following, we will refer to $c$ as the boundary factor of the approximation. The boundary factor can also be regarded as the boundary $L$ normalized by the half-range $S$ of the input space.

@@

As stated above, equations (\ref{eq_m_l_QE}), (\ref{eq_m_l_mat32}) and (\ref{eq_m_l_mat52}) (depending on which kernel is used) provide the minimum length-scale that can be closely approximated given $m$ and $c$. This information serves as a powerful diagnostic tool in determining if the obtained accuracy is acceptable. As the length-scale $\ell$ controls the wigglyness of the function, it strongly influences the difficulty of obtaining accurate inference about the function from the data. Basically, if the length-scale estimate is accurate, we can expect the HSGP approximation to be accurate as well.

@@

If the initial length-scale is not far from the optimal, and larger than minimal $c$ and $m$ are used in the initial HSGP model, it is likely that the initial results are already sufficiently accurate. The following iterative procedure works as safety approach and also allows finding a smaller sufficient $m$ which can be useful if the user wants to optimize the computational speed for repeated fitting (e.g., in cross-validation or simulation based calibration).

>>>>

In this work, we choose $L$ such that the domain $\Omega = \left[-L, L\right]$ contains all the inputs points $x_i$. Without loss of generality, we can assume all data points are contained in a symmetric interval around zero. Let $S = \max_{i}|x_i|$, then it follows that $x_i \in \left[-S, S\right]$ for all $i$. We now define $L$ as
\begin{equation}\label{eq_boundary}
L=c \cdot S,
\end{equation} 
%
where $S > 0$ represents the half-range of the input space, and $c \geq 1$ is the proportional extension factor. In the following, we will refer to $c$ as the boundary factor of the approximation. The boundary factor can also be regarded as the boundary $L$ normalized by the half-range $S$ of the input space.

@@

As stated above, equations (\ref{eq_m_l_QE}), (\ref{eq_m_l_mat32}) and (\ref{eq_m_l_mat52}) (depending on which kernel is used) provide the minimum length-scale that can be closely accurately given $m$ and $c$. This information serves as a powerful diagnostic tool in determining if the obtained accuracy is acceptable. As the length-scale $\ell$ controls the wigglyness of the function, it strongly influences the difficulty of estimating the latent function from the data. Basically, if the length-scale estimate is accurate, we can expect the HSGP approximation to be accurate as well.

@@

If the initial length-scale is not far from the optimal, and larger than the minimal $c$ and $m$ used in the initial HSGP model, it is likely that the initial results are already sufficiently accurate. The following iterative procedure works as safety approach and also allows finding a smaller sufficient $m$ which can be useful if the user wants to optimize the computational speed for repeated fitting (e.g., in cross-validation or simulation based calibration).
